systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-07-04 paper/trunk/JSS/response_B.tex

We have included a brief statement that the number of observations for
each equation in the system is the same.

\subsection{x and y variables}
% Page 2: It should be clarified whether y-variables in one equation can be x-variables in another.

This is stated in the introduction (page 2, lines 14-15).

\subsection{Instrumental variables}
% Page 4, line 82: 'may' should be 'must'. Here the difference is extremely important.

According to the comment of this referee,
we have replaced °may° by °must°.

% Maybe the text
% could emphasize more clearly what is required of a variable if it is to be used as an instrumental
% variable. What is a good instrumental variable and what happens if the requirements are not
% fulfilled?

@@

\subsection{First step OLS}
% Line 196: It should be explained what is meant by a first step OLS.

We have explained the two-step procedure
to obtain the estimated residual covariance matrix
more clearly now.

\subsection{Efficiency and maximum likelihood}
% Section 2.3: Somewhere in this section or (2.1) it should be noted that the efficiency results of
% section 2.1 depend on Sigma being known. And that a full maximum likelihood analysis may be
% superior.

We have noted that the GLS estimator (with known $\Sigma$) is efficient,
but the FGLS estimator (with unknown $\Sigma$)
is only \emph{asymptotically} efficient.
Since the iterated SUR (FGLS) estimator converges to FIML results,
the FIML method is not more efficient than iterated SUR (FGLS).

### 2007-07-04 paper/trunk/systemfit_estimation.tex
made clearer that GLS is efficient, but FGLS is only asymptotically efficient (suggested by referee B); added answer to referee B that we have done this
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@792 591db2bd-e0a0-4d22-8c19-2192dbb7da31

Like the OLS estimates, these estimates are only efficient
if the disturbance terms are not contemporaneously correlated.
An estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat \left[ \bHat_{WLS} \right] = \left( X' \OHat^{-1} X \right)^{-1} .
\end{equation}
If no cross-equation parameter restrictions are imposed,
the parameter estimates are equal to the OLS estimates.

@@

When the disturbances are contemporaneously correlated, a Generalized 
Least Squares (GLS) estimation leads to efficient parameter estimates.
In this case, the GLS estimator is generally called °Seemingly Unrelated Regression°
(SUR) estimator \citep{zellner62}.
Since the true covariance matrix of the disturbance terms
is generally unknown,
a Feasible Generalized Least Squares (FGLS) estimation,
which is based on an estimated covariance matrix of the disturbance terms,
is the textbook solution for this problem.
It should be noted that while an unbiased OLS or WLS estimation requires only that
the regressors and the disturbance terms of each single 
equation are uncorrelated
$( \E \left[ u_i ' X_i \right] = 0 \; \forall \; i )$,
a consistent SUR estimation requires that all disturbance terms and all 
regressors are uncorrelated
$( \E \left[ u_i ' X_j \right] = 0 \; \forall \; i, j )$.

>>>>

These estimates are (asymptotically) efficient
if the disturbance terms are not contemporaneously correlated.
An estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat \left[ \bHat_{WLS} \right] = \left( X' \OHat^{-1} X \right)^{-1} .
\end{equation}
If no cross-equation parameter restrictions are imposed,
the parameter estimates are equal to the OLS estimates.

@@

When the disturbances are contemporaneously correlated, a Generalized 
Least Squares (GLS) estimation leads to efficient parameter estimates.
In this case, the GLS estimator is generally called °Seemingly Unrelated Regression°
(SUR) estimator \citep{zellner62}.
However, the true covariance matrix of the disturbance terms
is generally unknown.
The textbook solution for this problem is
a Feasible Generalized Least Squares (FGLS) estimation.
As the FGLS estimator is based on
an estimated covariance matrix of the disturbance terms,
it is only asymptotically efficient.
It should be noted that while an unbiased OLS or WLS estimation requires only that
the regressors and the disturbance terms of each single 
equation are uncorrelated
$( \E \left[ u_i ' X_i \right] = 0 \; \forall \; i )$,
a consistent SUR estimation requires that all disturbance terms and all 
regressors are uncorrelated
$( \E \left[ u_i ' X_j \right] = 0 \; \forall \; i, j )$.
